Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-07 paper.tex
future work

\begin{figure}[htb]
  \centering
  \subfigure[Original in version XXXXXXXXXXXXXXXXXXXXXX]{
    \includegraphics[width=\linewidth]{images/os-orig.png}
    \label{subfig:os-orig}
   }
   \quad
  \subfigure[With GPGPU developed module]{
    \includegraphics[width=\linewidth]{images/os1.jpg}
    \label{subfig:os-mod}
   }
  \caption{Openstack Architecture}
  \label{fig:os}
\end{figure}

@@

\section{\uppercase{Future work}}
\label{sec:future}

>>>>

\begin{figure}[htb]
  \centering
  \subfigure[Original in version XXXXXXXXXXXX]{
    \includegraphics[width=\linewidth]{images/os-orig.png}
    \label{subfig:os-orig}
   }
   \quad
  \subfigure[With GPGPU developed module]{
    \includegraphics[width=\linewidth]{images/os1.jpg}
    \label{subfig:os-mod}
   }
  \caption{Openstack Architecture}
  \label{fig:os}
\end{figure}

@@

\section{\uppercase{Future work}}
\label{sec:future}
The first task that we should have keep in mind after this study is to upgrade the interconnection network to one more focused on HPC.
So that, porting the setup and the tests to an infrastructure with an Infiniband network would shed light on the viability of this kind of solutions for HPC.

Looking for real situations where the performance is not so important as the flexibility to provide more accelerators. 
Because of that, to take the first steps through how to deploy programming computer labs easily, could be really interesting.

Finally, to bring in more policies to decide the strategy of creating and assigning remote GPUs in the physical device, would be a task to increase the flexibility given by the GPGPU module for Openstack.
